Distinction Centrality Analysis

### 2025-07-20 analysis.qmd
captions

```{r Toy Network Distinction Tables}
    tab.cent(distinction(g1), name = "star", label = "tab:star")
    tab.cent(distinction(g2), name = "structfold", label = "tab:sf")
    tab.cent(distinction(g3), name = "intraclust", label = "tab:intra")
    tab.cent(distinction(g4), name = "interclust", label = "tab:inter")
    tab.cent(distinction(g5), name = "circle", label = "tab:circle")
    tab.cent(distinction(g6), name = "circletriangle", label = "tab:circletriangle")
    tab.cent(distinction(g7), name = "circlelong", label = "tab:circlelong")
    tab.cent(distinction(g8), name = "clique", label = "tab:clique")
    tab.cent(distinction(g9), name = "kite", label = "tab:kite")
    tab.cent(distinction(g10), name = "wheel", label = "tab:wheel")
```

>>>>

```{r Toy Network Distinction Tables}
   source(here("Functions", "tab.cent.R"))
   tab.cent(distinction(g1), name = "star", 
   label = "tab:star", rownames = c("1", "2, 3, 4, 5, 6, 7"),
   caption = "Distinction centrality scores for star graph.")
   tab.cent(distinction(g2), name = "structfold", 
   label = "tab:sf", rownames = c("1", "2, 3, 4, 5, 6, 7"),
   caption = "Distinction centrality scores for structural fold graph.")
   tab.cent(distinction(g3), name = "intraclust", 
   label = "tab:intra", , rownames =  c("1", "2, 3, 6, 7", "4, 5"),
   caption = "Distinction centrality scores for intra-connected clusters graph.")
   tab.cent(distinction(g4), name = "interclust", 
   label = "tab:inter", rownames =  c("1", "2, 7", "3, 6", "4, 5"),
   caption = "Distinction centrality scores for inter-connected clusters graph.")
   tab.cent(distinction(g5), name = "circle", 
   label = "tab:circle", rownames = c("1, 2, 3, 4, 5, 6, 7"),
   caption = "Distinction centrality scores for circle graph.")
   tab.cent(distinction(g6), name = "circletriangle", 
   label = "tab:circletriangle",  rownames = c("1, 6", "2, 5", "3, 4", "7"),
   caption = "Distinction centrality scores for circle graph with triangle.")
   tab.cent(distinction(g7), name = "circlelong", 
   label = "tab:circlelong", rownames = c("1, 3", "2", "4, 7", "5, 6"),
   caption = "Distinction centrality scores for circle graph with long tie.")
   tab.cent(distinction(g8), name = "clique", 
   label = "tab:clique", rownames = c("1, 2, 3, 4, 5, 6, 7"),
   caption = "Distinction centrality scores for clique graph.")
   tab.cent(distinction(g9), name = "kite", 
   label = "tab:kite", rownames = c("1", "2, 3, 4, 5, 6", "7"),
   caption = "Distinction centrality scores for kite graph.")
   tab.cent(distinction(g10), name = "wheel", 
   label = "tab:wheel", rownames = c("1", "2, 3, 4, 5, 6, 7"),
   caption = "Distinction centrality scores for wheel graph.")

```
